Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-09 surfaces-write-up/surface-write-up.tex
reworded further quesitons again

Every rational surface can be obtained from a minimal rational surface by a 
sequence of blow-ups \cite{eisenbud-harris:minimal}. Therefore, to answer
Question \ref{qn:general-minimal-surface} affirmatively, it suffices
to bound the degree of generators and relations of the 
canonical ring of a divisor on a blow-up of that surface $S$ in terms of 
the canonical
rings of some associated divisors on $S$.

>>>>

Every rational surface can be obtained from a minimal rational surface by a 
sequence of blow-ups \cite{eisenbud-harris:minimal}. Therefore, to answer
Question \ref{qn:general-minimal-surface} affirmatively, it suffices
to bound the degree of generators and relations of the 
canonical ring of a divisor on a blow-up of a given surface
in terms of the canonical
rings of some associated divisors that given surface.
